\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-07-27 sections/methods.tex
Add data visualizer section to methods

>>>>

  \subsubsection*{MIND Data Visualizer}

    In addition to the web application and pipeline, we have also developed a tool that facilitates easy visualization and exploration of the data generated by the \ac{mind} pipeline.
    This tool is a Python package and is built using dash \cite{dash}.
    It aids in the analysis of the effects of different processing methods on the generated counts matrix or network.
    It takes in as input the results of a pipeline run and allows one to visualize various properties of intermediate \ac{otu} or \ac{esv} tables and final association networks.
    This tool makes it easy and straightforward to compare different methods and combinations of methods in the 16S data analysis workflow.

    The visualization tool currently supports:
    \begin{itemize}
      \item Filtering and aggregating data from multiple sources (data-sets)
      \item Comparing properties of the generated counts matrices and networks across different methods
      \item Visualization of these properties
    \end{itemize}
